\mytitle

### 2020-05-04 paper.tex
Add formula for temperature decay rate.

For exact methods (QP-SS, ILP-LS, QP-LS and QUBO-LS),
we ran Gurobi with a time limit of 3600 seconds. We collected all feasible solutions
found until that point in time.
%The best solution in terms of energy is the solution that attained the highest objective
%values (SS in QP-SS and LS in the rest of the methods).
For the DA, we used a single configuration that was found to work best across the different instances. The initial temperature is 500000, the temperature mode is 0, the  interval for updating is 1, the offset increase rate is 10, the number of runs is 20, and the temperature decay rate is computed dynamically. \todo{Eldan and Arik: Do I need to write the formula for computing temperature decay rate? -- Jason} \todo{JCB: Yes, if it is not too complicated. You should mention if this is the standard thing that DA does or something you came up with.} The DA ran until convergence of the underlying simulated annealing algorithm and the runtime 
of the procedure was recorded. \todo{\\EC: I am not sure what does it mean for the DA to run until convergence. You may want to specify that the DA was run with increasingly large time limits until no further improvement in objective.\\}

>>>>

For exact methods (QP-SS, ILP-LS, QP-LS and QUBO-LS),
we ran Gurobi with a time limit of 3600 seconds. We collected all feasible solutions
found until that point in time.
%The best solution in terms of energy is the solution that attained the highest objective
%values (SS in QP-SS and LS in the rest of the methods).
For the DA, we used a single configuration that was found to work best across the different instances. The initial temperature \text{tmp\_st} is 500000, the temperature mode is 0, the interval \text{tmp\_interval} for updating is 1, the offset increase rate is 10, the number of runs is 20, and the temperature decay rate is computed dynamically, i.e., $ \text{tmp\_decay} = (0.001 / \text{tmp\_st})^{(1.0 / (\text{num\_iterations} / \text{tmp\_interval}))} $. This formula of decay rate is for better convergence and is provided by DA developers. \todo{JCB: Yes, if it is not too complicated. You should mention if this is the standard thing that DA does or something you came up with.} The DA ran until convergence of the underlying simulated annealing algorithm and the runtime 
of the procedure was recorded. \todo{\\EC: I am not sure what does it mean for the DA to run until convergence. You may want to specify that the DA was run with increasingly large time limits until no further improvement in objective.\\}
